### 2018-09-14 algorithm.tex
close #14: calibrate US productivity to real GDP

Fourth, for services, we calculate the demand shifter as 
\[
\nu_{nJt} = 1-\sum_{j\neq J}\nu_{njt},
\]
and construct its prices as
\[
P_{nJt} = (\nu_{nJt}/e_{nJt})^{1/(\sigma-1)} P_{0t}PWT_{nt}.
\]
This is the only step that has to be done separately for $\sigma=1$, although approximations may be valid. CHECK.
\end{document}

>>>>

Fourth, for services, we calculate the demand shifter as 
\[
\nu_{nJt} = 1-\sum_{j\neq J}\nu_{njt},
\]
and construct its prices as
\[
P_{nJt} = (\nu_{nJt}/e_{nJt})^{1/(\sigma-1)} P_{0t}PWT_{nt}.
\]
This is the only step that has to be done separately for $\sigma=1$, although approximations may be valid. CHECK.

Computing the price index for US, 1972,
\begin{equation}
	\left[\sum_{j=1}^J \nu_{US,jt} 1^{1-\sigma}\right]^{1/(1-\sigma)} = 
	\left[\sum_{j=1}^J \nu_{US,jt}\right]^{1/(1-\sigma)}
 =1,
\end{equation}
so we are measuring all nominal quantities in 1972 US dollars.

\subsection{Calibrating US productivity}
Import shares are only informative about relative productivities. For a benchmark country, the US, we calibrate productivity to match observed value added data. Using \eqref{eq:wage}, we can express productivity as a function of sectoral wages,
\begin{equation*}\label{eq:value_added}
A_{njt} =
	\xi B_j
	w_{njt}^{\beta_j}
	\varrho_{njt}^{-1}  	
	\prod_{k=1}^J P_{nkt}^{\gamma_{kj}},
\end{equation*}
and
\[
d_{nnjt} = (\varrho_{njt}/P_{njt})^{-\theta}
\]
can be used to express
\[
\varrho_{njt} = P_{njt} d_{nnjt}^{-1/\theta}.
\]
\begin{equation}\label{eq:productivity}
A_{njt} =
	\xi B_j
	d_{nnjt}^{1/\theta}
	(w_{njt}/P_{njt})^{\beta_j}
 	\prod_{k=1}^J (P_{nkt}/P_{njt})^{\gamma_{kj}}.
\end{equation}
Productivity is high when domestic market share is high, when real wages in sector are high, or when real input costs are high.

Assume that the US is in a flexible-labor equilibrium in every period so that 
\[
w_{njt} = w_{nt},
\]
nominal GDP. 
\end{document}
